 In excercises $1$ to $8$, find the equation of the line which satisfy  the given conditions:
\begin{enumerate}
\item Write the equations for $x$ and $y$ axes.
\item Passing through the point $(-4,3)$ with slope $\frac {1}{2}$.
\item Passing through $(0,0)$ with slope $m$.
\item Passing through $(2,\sqrt {3})$ and inclined with $x$ axis at an angle of $75\degree$.
\item Intersecting the $x$ axis at a distance of $3$ units to the left of the origin with slope $-2$.
\item Intersecting the $y$ axis at a distance of $2$ units above the origin and making an angle of $30°$ with positive direction of the $x$ axis.
\item Passing through the points $(-1,1)$ and $(2,-4)$.
\item Perpendicular distance from the origin is $5$ units and the angle made by the perpendicular with the positive $x$ axis is $30°$. 
\item The vertices of $\triangle PQR$ are $P(2,1), Q(-2,3)$ and $R(4,5)$. Find equation of the median through the vertex $R$.
\item Find the equation of the line passing through $(-3,5)$ and perpendicular to the line through the points $(2,5)$ and $(-3,6)$.
\item A line perpendicular to the line segment joining the points $(1,0)$  and $(2,3)$ divides it in the ratio $1:n$. Find the equation of the line.
\item Find the equation of the line that cuts off equal axes and passes through the point $(2,3)$.
\item Find equation of the line passing through the point $(2,2)$ and cutting off intercepts on the axes whose sum is $9$.
\item Find equation of the line through the point $(0,2)$ making an angle $\frac{2\pi}{3}$ with the positive $x$ axis. Also, find the equation of the parallel to it and crossing the $y$ axis at a distance of $2$ units below the origin.
\item The perpendicular from the origin to a line meets it at the point $(-2,9)$, find the equation of the line.
\item The length $L$ [in centimetre of a copper rod is a linear function of its celsius temperature $C$]. In an experiment, if $L=124.942$. When $C=20$  and $L=125.134$ When $C=110$, express $L$ in terms of $C$.
\item The owner of a milk store finds that, he can sell $980$ litres of milk each week at \rupee~14/litre and $1220$ litres of milk each week at \rupee~16/litre. Assuming a linear relationship between selling price and demand, how many litres could he sell weekly at \rupee~17/ litre?
\item $P(a,b)$ is the mid-point of a line segment between axes. Show that equation of the line is $\frac{x}{a}+\frac{y}{b}=2$
\item Point $R(h,k)$ divides a line segment betwween the axes in the ratio $1:2$. find equation of the line.
\item By Using the concept of equation of a line, prove that the three points (3,0), (-2,-2) and (8,2) are collinear.
\end{enumerate}

