\begin{enumerate}
\item Which of the following pairs of linear equations has unique solution, no solution or infinitely many solutions.In case there is a unique solution,find it by using cross multiplication method:
  \begin{enumerate}[label=(\roman*)]
	\item \begin{align}
	x-3y-3=0\\
	3x-9y-2=0
        \end{align}
       \item \begin{align}
	2x+y=5\\
	3x+2y=8
	\end{align}
	\item \begin{align}
	3x-5y=20\\
	6x-10y=40
	\end{align}
	\item \begin{align}
	x-3y-7=0\\
	3x-3y-15=0
        \end{align}
 \end{enumerate}
\item 
  \begin{enumerate}[label=(\roman*)]
  \item For which values of $a$ and $b$ does the following pair of linear equations have an infinite number of solutions?
	\begin{align}
	2x+3y=7\\
	(a-b)x+(a-b)y=3a+b-2
	\end{align}
  \item For which value of $k$ will the following pair of linear equation have no solution?
	\begin{align}
	3x+y=1\\
	(2k-1)x+(k-1)y=2k+1
	\end{align}
   \end{enumerate}
\item Solve the following pair of linear equations by the substituions and cross multiplication method:
\begin{align}
8x+5y=9
\\ 3x+2y=4
\end{align}
\item Form the pair of linear equations in the following problems and find their solutions by any algebraic method:
\begin{enumerate}[label=(\roman*)]
\item A part of monthly hostel charges is fixed and the remaining depends on the number of days one has taken food in the mess. When a student $A$ takes food for $20$ days she has to pay Rs.$1000$ as hostel charges whereas a student $B$ who takes food for $26$ days, pays Rs.$1180$ as hostel charges. Find the fixed charges and the cost of food per day.
\item A fraction becomes $\frac{1}{3}$ when $1$ is subtracted from the numerator and it becomes $\frac{1}{4}$ when $8$ is added to the denominator. Find the fraction.
\item Yash scored $40$ marks in a test, getting $3$ marks for each right answer and losing $1$ mark for each wrong answer. Had $4$ marks been awarded for each correct answer and $2$ marks been deducted for each incorrect answer, then Yash would have scored $50$ marks. How many questions were there in the test?
\item Places $A$ and $B$ are $100km$ apart on a highway. One car starts from $A$ and another from $B$ at the same time. If the car travel in the same direction at different speeds, they meet in $5$hrs. If they travel towards each other, they meet in $1$hr. What are the speeds of the two cars?
\item The area of rectangle gets reduced by $9$ square units, if its length is reduced by $5$ units and breadth is increased by $3$ units. If we increase the length by $3$ units and the breadth by $2$ units, the area increases by $67$ square units. Find the dimensions of the rectangle.
\end{enumerate}
\end{enumerate}
