\begin{enumerate}
\item  Find the roots of the following quadratic  equations by factorisation:
\begin{enumerate}[label=(\roman*)]
\item $x^2-3x-10=0$
\item $2x^2+x-6=0$
\item $ \sqrt 2x^2+7x+5 \sqrt 2=0$
\item $2x^2-x+\frac{1}{8}=0$
\item $100x^2-20x+1=0$
\end{enumerate}
\item Represent the following situations mathematically;
\begin{enumerate}[label=(\roman*)]
\item John and Jivanti together have $45$ marbles. Both of them lost $5$ marbles each, and the product of the number of marbles they have is $124$. We would like to find out how many marbles they had to start with.
\item A cottage industry produces a certain number of toys in a day. The cost of production of each toy (in rupees) was found to be $55$ minus the number of toys produced in a day. On a particular day, the total cost of production was \rupee~750. We would like to find out the number of toys produced on that day.
\end{enumerate}
\item Find two numbers whose sum is $27$ and product is $182$.
\item Find two consecutive  positive integers, sum of whose squares is $365$.
\item  The altitude of a right triangle is 7 cm less than its base. If the hypotenuse is 13 cm, find the other two sides.
\item A cottage industry produces a certain number of pottery articles in a day. It was observed on a particular day that the cost of production of each article (in rupees) was $3$ more than twice the number of articles produced on that day. If the total cost of production on that day was \rupee~90, find the number of articles produced and the cost of each article.
\end{enumerate}

